---
title: "Mass Dynimics QC-Report"
output:
  html_document:
    code_folding: hide
    theme: united
    toc: yes
    toc_float: yes
    self_contained: true
    fig_caption: yes
  pdf_document:
    toc: yes
---
```{r, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)

num_files <- expdes[, .N]
run_per_condition <- expdes[, .(countRepMax = .N), by = .(experiment)]
setnames(run_per_condition, "experiment", "condition")

mod_pept_int_rep <- merge(
  run_per_condition,
  mod_pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
mod_pept_int_rep[, repPC := Repcount/countRepMax]
mod_pept_id_in_a_cond <- mod_pept_int_rep[repPC >= 0.5, unique(id)]
mod_pept_int[, Valid := 0L]
mod_pept_int[id %in% mod_pept_id_in_a_cond, Valid := 1L]
rm(mod_pept_id_in_a_cond, mod_pept_int_rep)

pept_int_rep <- merge(
  run_per_condition,
  pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
pept_int_rep[, repPC := Repcount/countRepMax]
pept_id_in_a_cond <- pept_int_rep[repPC >= 0.5, unique(id)]
pept_int[, Valid := 0L]
pept_int[id %in% pept_id_in_a_cond, Valid := 1L]
rm(pept_id_in_a_cond, pept_int_rep)

prot_int_rep <- merge(
  run_per_condition,
  prot_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
prot_int_rep[, repPC := Repcount/countRepMax]
prot_id_in_a_cond <- prot_int_rep[repPC >= 0.5, unique(id)]
prot_int[, Valid := 0L]
prot_int[id %in% prot_id_in_a_cond, Valid := 1L]
rm(prot_id_in_a_cond, prot_int_rep)


```


# 1. Experiment Health

## A. Principal Component Analysis (PCA) and Dimensionality Reduction {.tabset .tabset-fade .tabset-pills}

### Proteins

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
# Prepare PCA data table
# limiting the data by number of missing values as per input parameters:
# limitImputedRatio
# checkBy

if (checkBy == "Experiment") {
  pca_dt <- prot_int[Valid == 1, .(
    id,
    condition,
    Replicate,
    log2NInt,
    run_id
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

} else {
  # pca_dt <- prot_int[Valid == 1, .(
  #   id,
  #   condition,
  #   Replicate,
  #   log2NInt,
  #   run_id
  # )]
  # pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")
  #
  print("ERROR")
}

num_dimensions = min(pca_dt[, .N-1], 10)
res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
eig.val <- get_eigenvalue(res.pca)
eig.val <- data.table(dims = rownames(eig.val), eig.val)

samples.pca <- get_pca_ind(res.pca)
samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
  stat_ellipse(geom = "polygon", alpha=0.1) +
  geom_point(size = 3, alpha = 0.7) +
  theme_minimal() +
  scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
  scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%"))

ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

scree_plot <- ggplot(eig.val[1:num_dimensions], aes(x=reorder(dims, -`variance.percent`), y=`variance.percent`)) +
  geom_bar(stat="identity", fill = "skyblue2") +
  theme_minimal() +
  geom_text_repel(aes(label=(round(`variance.percent`,1))), direction = 'y') +
  scale_x_discrete("PCA components") +
  scale_y_continuous("% Variance") +
  ggtitle("Scree plot")
scree_plot

name_of_column <- colnames(prot)[colnames(prot) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && prot[get(name_of_column) <= 0.05, .N] > 1) {
  DE_ids <- prot[get(name_of_column) <= 0.05, unique(id)]
  pca_dt <- prot_int[id %in% DE_ids, .(
    id,
    condition,
    Replicate,
    log2NInt
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

  num_dimensions = min(pca_dt[, .N-1], 10)
  res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
  eig.val <- get_eigenvalue(res.pca)
  eig.val <- data.table(dims = rownames(eig.val), eig.val)

  samples.pca <- get_pca_ind(res.pca)
  samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
  samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

  p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
    stat_ellipse(geom = "polygon", alpha=0.1) +
    geom_point(size = 3, alpha = 0.7) +
    theme_minimal() +
    scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
    scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%")) +
    ggtitle(str_c("PCA plot using the ", length(DE_ids), " differencially expressed proteins"))
  ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

}
```

### Modification specific peptides
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
# Prepare PCA data table
# limiting the data by number of missing values as per input parameters:
# limitImputedRatio
# checkBy

if (checkBy == "Experiment") {
  pca_dt <- mod_pept_int[Valid == 1, .(
    id,
    condition,
    Replicate,
    log2NInt,
    run_id
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

} else {
  # pca_dt <- mod_pept_int[Valid == 1, .(
  #   id,
  #   condition,
  #   Replicate,
  #   log2NInt,
  #   run_id
  # )]
  # pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")
  #
  print("ERROR")
}

num_dimensions = min(pca_dt[, .N-1], 10)
res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
eig.val <- get_eigenvalue(res.pca)
eig.val <- data.table(dims = rownames(eig.val), eig.val)

samples.pca <- get_pca_ind(res.pca)
samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
  stat_ellipse(geom = "polygon", alpha=0.1) +
  geom_point(size = 3, alpha = 0.7) +
  theme_minimal() +
  scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
  scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%"))

ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

scree_plot <- ggplot(eig.val[1:num_dimensions], aes(x=reorder(dims, -`variance.percent`), y=`variance.percent`)) +
  geom_bar(stat="identity", fill = "skyblue2") +
  theme_minimal() +
  geom_text_repel(aes(label=(round(`variance.percent`,1))), direction = 'y') +
  scale_x_discrete("PCA components") +
  scale_y_continuous("% Variance") +
  ggtitle("Scree plot")
scree_plot

name_of_column <- colnames(mod_pept)[colnames(mod_pept) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && mod_pept[get(name_of_column) <= 0.05, .N] > 1) {
  DE_ids <- mod_pept[get(name_of_column) <= 0.05, unique(id)]
  pca_dt <- mod_pept_int[id %in% DE_ids, .(
    id,
    condition,
    Replicate,
    log2NInt
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

  num_dimensions = min(pca_dt[, .N-1], 10)
  res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
  eig.val <- get_eigenvalue(res.pca)
  eig.val <- data.table(dims = rownames(eig.val), eig.val)

  samples.pca <- get_pca_ind(res.pca)
  samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
  samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

  p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
    stat_ellipse(geom = "polygon", alpha=0.1) +
    geom_point(size = 3, alpha = 0.7) +
    theme_minimal() +
    scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
    scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%")) +
    ggtitle(str_c("PCA plot using the ", length(DE_ids), " differencially expressed peptides"))
  ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

}

```


### Peptides

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
# Prepare PCA data table
# limiting the data by number of missing values as per input parameters:
# limitImputedRatio
# checkBy

if (checkBy == "Experiment") {
  pca_dt <- pept_int[Valid == 1, .(
    id,
    condition,
    Replicate,
    log2NInt,
    run_id
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

} else {
  # pca_dt <- pept_int[Valid == 1, .(
  #   id,
  #   condition,
  #   Replicate,
  #   log2NInt,
  #   run_id
  # )]
  # pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")
  #
  print("ERROR")
}

num_dimensions = min(pca_dt[, .N-1], 10)
res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
eig.val <- get_eigenvalue(res.pca)
eig.val <- data.table(dims = rownames(eig.val), eig.val)

samples.pca <- get_pca_ind(res.pca)
samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
  stat_ellipse(geom = "polygon", alpha=0.1) +
  geom_point(size = 3, alpha = 0.7) +
  theme_minimal() +
  scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
  scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%"))

ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

scree_plot <- ggplot(eig.val[1:num_dimensions], aes(x=reorder(dims, -`variance.percent`), y=`variance.percent`)) +
  geom_bar(stat="identity", fill = "skyblue2") +
  theme_minimal() +
  geom_text_repel(aes(label=(round(`variance.percent`,1))), direction = 'y') +
  scale_x_discrete("PCA components") +
  scale_y_continuous("% Variance") +
  ggtitle("Scree plot")
scree_plot

name_of_column <- colnames(pept)[colnames(pept) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && pept[get(name_of_column) <= 0.05, .N] > 1) {
  DE_ids <- pept[get(name_of_column) <= 0.05, unique(id)]
  pca_dt <- pept_int[id %in% DE_ids, .(
    id,
    condition,
    Replicate,
    log2NInt
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")

  num_dimensions = min(pca_dt[, .N-1], 10)
  res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
  eig.val <- get_eigenvalue(res.pca)
  eig.val <- data.table(dims = rownames(eig.val), eig.val)

  samples.pca <- get_pca_ind(res.pca)
  samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
  samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]

  p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
    stat_ellipse(geom = "polygon", alpha=0.1) +
    geom_point(size = 3, alpha = 0.7) +
    theme_minimal() +
    scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
    scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%")) +
    ggtitle(str_c("PCA plot using the ", length(DE_ids), " differencially expressed peptides"))
  ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = F)

}

```


## B. Quantitative values CV distributions {.tabset .tabset-fade .tabset-pills}

### Proteins

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
cvdt <- prot_int[Imputed == 0][, countRep := .N, by = .(id, condition)]
cvdt[, countRepMax := max(countRep), by = .(id, condition)]
cvdt[, ReplicatePC := countRep/countRepMax]
cvdt[, intensity := as.double(intensity)]
cvdt <- cvdt[ReplicatePC >= 0.5, .(cv = sd(intensity)/mean(intensity)), by = .(id, condition)]

ggplotly(ggplot(cvdt, aes(x=cv, fill=condition, colour=condition)) +
  geom_density(alpha=0.4) +
  theme_minimal() +
  scale_x_continuous("% CV", labels = scales::percent) +
  ggtitle("Proteins - LFQ intensity CV")) %>% config(displayModeBar = F)
```


### Modification specific peptides

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
cvdt <- mod_pept_int[Imputed == 0][, countRep := .N, by = .(id, condition)]
cvdt[, countRepMax := max(countRep), by = .(id, condition)]
cvdt[, ReplicatePC := countRep/countRepMax]
cvdt[, intensity := as.double(intensity)]
cvdt <- cvdt[ReplicatePC >= 0.5, .(cv = sd(intensity)/mean(intensity)), by = .(id, condition)]

p <- ggplot(cvdt, aes(x=cv, fill=condition, colour=condition)) +
  geom_density(alpha=0.4) +
  theme_minimal() +
  scale_x_continuous("% CV", labels = scales::percent) +
  ggtitle("Modification specific peptides - intensity CV")
ggplotly(p) %>% config(displayModeBar = F)
```


### Peptides

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
cvdt <- pept_int[Imputed == 0][, countRep := .N, by = .(id, condition)]
cvdt[, countRepMax := max(countRep), by = .(id, condition)]
cvdt[, ReplicatePC := countRep/countRepMax]
cvdt[, intensity := as.double(intensity)]
cvdt <- cvdt[ReplicatePC >= 0.5, .(cv = sd(intensity)/mean(intensity)), by = .(id, condition)]

p <- ggplot(cvdt, aes(x=cv, fill=condition, colour=condition)) +
  geom_density(alpha=0.4) +
  theme_minimal() +
  scale_x_continuous("% CV", labels = scales::percent) +
  ggtitle("Peptide - LFQ intensity CV")
ggplotly(p) %>% config(displayModeBar = F)
```


## B. Sample and Intensity Correlation Plots {.tabset .tabset-fade .tabset-pills}

### Proteins

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

filenames <- prot_int[!(is.na(file_name)), unique(run_id)]

int_corr_dt <- dcast.data.table(
  prot_int[Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)
DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
DT_corMatrix <- DT_corMatrix$r
DT_corMatrix[DT_corMatrix <= -1] = -1
DT_corMatrix[DT_corMatrix >= 1] = 1
#corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))
if (num_files > 10) {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))

} else {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

}

name_of_column <- colnames(prot)[colnames(prot) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && mod_pept[get(name_of_column) <= 0.05, .N] > 4) {
  # DE_ids <- prot[get(name_of_column) <= 0.05, unique(ProteinGroupId)]
  DE_ids <- prot[get(name_of_column) <= 0.05, unique(id)]
  int_corr_dt <- int_corr_dt[id %in% DE_ids]
  DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
  DT_corMatrix <- DT_corMatrix$r

  DT_corMatrix[DT_corMatrix <= -1] = -1
  DT_corMatrix[DT_corMatrix >= 1] = 1

  if (num_files > 10) {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0))

  } else {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

  }
}


if (length(filenames) > 4) {
  filenames <- sample(filenames, 4)
}

int_corr_dt <- dcast.data.table(
  prot_int[run_id %in% filenames & Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)

myplot <- function(data, mapping, ...) {
  ggplot(data=data, mapping=mapping) +
  geom_point(size = 1, alpha = 0.3, colour = "skyblue2") +
  theme_minimal()
}
p <- ggpairs(int_corr_dt, columns = colnames(int_corr_dt)[2:ncol(int_corr_dt)],
        upper = list(
    continuous = myplot
  ),
  lower = "blank",
  diag = NULL
  )
p
```


### Modification specific peptides

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

filenames <- mod_pept_int[!(is.na(file_name)), unique(run_id)]

int_corr_dt <- dcast.data.table(
  mod_pept_int[Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)
DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
DT_corMatrix <- DT_corMatrix$r
DT_corMatrix[DT_corMatrix <= -1] = -1
DT_corMatrix[DT_corMatrix >= 1] = 1
#corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))
if (num_files > 10) {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))

} else {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

}

name_of_column <- colnames(mod_pept)[colnames(mod_pept) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && mod_pept[get(name_of_column) <= 0.05, .N] > 4) {
  # DE_ids <- prot[get(name_of_column) <= 0.05, unique(ProteinGroupId)]
  DE_ids <- mod_pept[get(name_of_column) <= 0.05, unique(id)]
  int_corr_dt <- int_corr_dt[id %in% DE_ids]
  DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
  DT_corMatrix <- DT_corMatrix$r

  DT_corMatrix[DT_corMatrix <= -1] = -1
  DT_corMatrix[DT_corMatrix >= 1] = 1

  if (num_files > 10) {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0))

  } else {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

  }
}


if (length(filenames) > 4) {
  filenames <- sample(filenames, 4)
}

int_corr_dt <- dcast.data.table(
  mod_pept_int[run_id %in% filenames & Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)

myplot <- function(data, mapping, ...) {
  ggplot(data=data, mapping=mapping) +
  geom_point(size = 1, alpha = 0.3, colour = "skyblue2") +
  theme_minimal()
}
p <- ggpairs(int_corr_dt, columns = colnames(int_corr_dt)[2:ncol(int_corr_dt)],
        upper = list(
    continuous = myplot
  ),
  lower = "blank",
  diag = NULL
  )
p
```


### Peptides

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

filenames <- pept_int[!(is.na(file_name)), unique(run_id)]

int_corr_dt <- dcast.data.table(
  pept_int[Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)
DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
DT_corMatrix <- DT_corMatrix$r
DT_corMatrix[DT_corMatrix <= -1] = -1
DT_corMatrix[DT_corMatrix >= 1] = 1
#corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))
if (num_files > 10) {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0))

} else {
  corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

}

name_of_column <- colnames(pept)[colnames(pept) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && mod_pept[get(name_of_column) <= 0.05, .N] > 4) {
  # DE_ids <- prot[get(name_of_column) <= 0.05, unique(ProteinGroupId)]
  DE_ids <- pept[get(name_of_column) <= 0.05, unique(id)]
  int_corr_dt <- int_corr_dt[id %in% DE_ids]
  DT_corMatrix <- rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)]))
  DT_corMatrix <- DT_corMatrix$r

  DT_corMatrix[DT_corMatrix <= -1] = -1
  DT_corMatrix[DT_corMatrix >= 1] = 1

  if (num_files > 10) {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0))

  } else {
    corrplot(DT_corMatrix, type = "upper", title = "Correlation Matrix - DE peptides", tl.cex = 0.5, mar = c(1,0,1.5,0), addCoef.col = "white", number.cex = .5)

  }
}


if (length(filenames) > 4) {
  filenames <- sample(filenames, 4)
}

int_corr_dt <- dcast.data.table(
  pept_int[run_id %in% filenames & Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)

myplot <- function(data, mapping, ...) {
  ggplot(data=data, mapping=mapping) +
  geom_point(size = 1, alpha = 0.3, colour = "skyblue2") +
  theme_minimal()
}
p <- ggpairs(int_corr_dt, columns = colnames(int_corr_dt)[2:ncol(int_corr_dt)],
        upper = list(
    continuous = myplot
  ),
  lower = "blank",
  diag = NULL
  )
p
```

# 2. Feature Completeness

## A. Data completeness {.tabset .tabset-fade .tabset-pills}

### Proteins
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}


dt <- unique(prot_int[Imputed == 0, .(ReplicatePC = .N/num_files), by = .(id)])

ymax <- max(dt[, .N, by = .(ReplicatePC)][, N])
ymax <- 0.01 * ymax + ymax

p <- ggplot(dt, aes(x = ReplicatePC)) +
  annotate('rect', xmin = 0.7, xmax = 1.05, ymin = 0, ymax = ymax, alpha=0.2)  +
  geom_histogram(binwidth = max(0.1, round(1/max(num_files), 2)), fill="skyblue2") +
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per protein", labels = scales::percent, limits = c(0, 1.15), breaks = seq(0, 1, 0.1)) +
  annotate('text', x = 0.5, y = 0.8*ymax, label=str_c("Number of proteins with\nmissing values <= 30%:\n ", dt[ReplicatePC >= 0.7, .N]))
ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = F)

dt <- prot_int[Imputed == 0, .(`% measured values` = .N/prot_int[, length(unique(id))]), by = .(run_id, condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

dt[, `% measured values` := 100*(round(`% measured values`, 2))]

p<- ggplot(dt, aes(x = `% measured values`, y = 1,  fill=condition, colour=condition, label=Run)) +
  geom_bar(colour="lightgray", stat="identity")+
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per LC-MS run", labels = function(x){paste(x, "%", sep = "")}, limits = c(-0.1, 100.1), breaks = seq(0, 100, 10)) +
  scale_y_continuous("Count")

ggplotly(p, tooltip = c("label", "x")) %>% config(displayModeBar = F)



```


### Modification specific peptides
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}


dt <- unique(mod_pept_int[Imputed == 0, .(ReplicatePC = .N/num_files), by = .(id)])

ymax <- max(dt[, .N, by = .(ReplicatePC)][, N])
ymax <- 0.01 * ymax + ymax

p <- ggplot(dt, aes(x = ReplicatePC)) +
  annotate('rect', xmin = 0.7, xmax = 1.05, ymin = 0, ymax = ymax, alpha=0.2)  +
  geom_histogram(binwidth = max(0.1, round(1/max(num_files), 2)), fill="skyblue2") +
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per peptide", labels = scales::percent, limits = c(0, 1.15), breaks = seq(0, 1, 0.1)) +
  annotate('text', x = 0.5, y = 0.8*ymax, label=str_c("Number of peptides with\nmissing values <= 30%:\n ", dt[ReplicatePC >= 0.7, .N]))
ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = F)

dt <- mod_pept_int[Imputed == 0, .(`% measured values` = .N/mod_pept_int[, length(unique(id))]), by = .(run_id, condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

dt[, `% measured values` := 100*(round(`% measured values`, 2))]

p<- ggplot(dt, aes(x = `% measured values`, y = 1,  fill=condition, colour=condition, label=Run)) +
  geom_bar(colour="lightgray", stat="identity")+
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per LC-MS run", labels = function(x){paste(x, "%", sep = "")}, limits = c(-0.1, 100.1), breaks = seq(0, 100, 10)) +
  scale_y_continuous("Count")

ggplotly(p, tooltip = c("label", "x")) %>% config(displayModeBar = F)



```


### Peptides
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}


dt <- unique(pept_int[Imputed == 0, .(ReplicatePC = .N/num_files), by = .(id)])

ymax <- max(dt[, .N, by = .(ReplicatePC)][, N])
ymax <- 0.01 * ymax + ymax

p <- ggplot(dt, aes(x = ReplicatePC)) +
  annotate('rect', xmin = 0.7, xmax = 1.05, ymin = 0, ymax = ymax, alpha=0.2)  +
  geom_histogram(binwidth = max(0.1, round(1/max(num_files), 2)), fill="skyblue2") +
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per peptide", labels = scales::percent, limits = c(0, 1.15), breaks = seq(0, 1, 0.1)) +
  annotate('text', x = 0.5, y = 0.8*ymax, label=str_c("Number of peptides with\nmissing values <= 30%:\n ", dt[ReplicatePC >= 0.7, .N]))
ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = F)

dt <- pept_int[Imputed == 0, .(`% measured values` = .N/pept_int[, length(unique(id))]), by = .(run_id, condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

dt[, `% measured values` := 100*(round(`% measured values`, 2))]

p<- ggplot(dt, aes(x = `% measured values`, y = 1,  fill=condition, colour=condition, label=Run)) +
  geom_bar(colour="lightgray", stat="identity") +
  theme_minimal() +
  scale_x_continuous("Percentage of measurements per LC-MS run", labels = function(x){paste(x, "%", sep = "")}, limits = c(-0.1, 100.1), breaks = seq(0, 100, 10)) +
  scale_y_continuous("Count")

ggplotly(p, tooltip = c("label", "x")) %>% config(displayModeBar = F)



```


# 3 Sample preparation

## Digestion efficiency

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(evidence)

setnames(dt, "experiment", "condition")
dt[is.na(condition), condition := "Library"]
dt[condition == "Library" & is.na(Replicate), Replicate := .GRP, by = .(`raw file`)]

if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
  dt <- dt[, .(count = .N), by = .(`missed cleavages`, condition, Replicate, fraction, `raw file`)]
  dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
  dt <- dt[, .(count = .N), by = .(`missed cleavages`, condition, Replicate, `raw file`)]
  dt[, Run := str_c(condition, Replicate, sep = " - ")]

}
dt[, `missed cleavages` := as.factor(`missed cleavages`)]

ggplot(dt, aes(x = Run, y = count,  fill=`missed cleavages`, label=Run)) +
  geom_bar(stat="identity", position=position_fill(reverse = TRUE)) + 
  theme_minimal() +
  scale_y_continuous("% missed cleavages", labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )

```


# 4. Identifications

## A. Counts {.tabset .tabset-fade .tabset-pills}

### Proteins

#### With intensity values - from proteinGroups.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(prot_int[Imputed == 0])

dt[is.na(condition), condition := "Library"]

if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0)]) {
dt <- dt[, .N, by = .(condition, Replicate, fraction)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- dt[, .N, by = .(condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=Replicate)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# PSMs") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))

```

#### all - from evidence.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(evidence)

setnames(dt, "experiment", "condition")
dt[is.na(condition), condition := "Library"]
dt[condition == "Library" & is.na(Replicate), Replicate := .GRP, by = .(`raw file`)]


if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- unique(dt[, .(`leading razor protein`, condition, Replicate, fraction, `raw file`)])[, .N, by = .(condition, Replicate, fraction, `raw file`)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- unique(dt[, .(`leading razor protein`, condition, Replicate,  `raw file`)])[, .N, by = .(condition, Replicate, `raw file`)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=`raw file`)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# PSMs") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))

```


### Modifiication specific peptides

#### all - from evidence.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
#dt <- merge(msms, unique(feature_quant_dt[, .(file_name, condition, Replicate)]), by = "file_name", all.x = T)
dt <- copy(evidence)


setnames(dt, "experiment", "condition")
dt[is.na(condition), condition := "Library"]
dt[condition == "Library" & is.na(Replicate), Replicate := .GRP, by = .(`raw file`)]


if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- unique(dt[, .(sequence, modifications, condition, Replicate, fraction, `raw file`)])[, .N, by = .(condition, Replicate, fraction, `raw file`)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- unique(dt[, .(sequence, modifications, condition, Replicate, `raw file`)])[, .N, by = .(condition, Replicate, `raw file`)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g<- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=`raw file`)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# Modified Sequences") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))

```

#### With intensity values - from modificationSpecificPeptides.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(mod_pept_int[Imputed == 0])

dt[is.na(condition), condition := "Library"]


if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- dt[, .N, by = .(condition, Replicate, fraction)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- dt[, .N, by = .(condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=Replicate)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# Modified Sequences") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))

```


### Peptides

#### all - from evidence.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

dt <- copy(evidence)

setnames(dt, "experiment", "condition")
dt[is.na(condition), condition := "Library"]
dt[condition == "Library" & is.na(Replicate), Replicate := .GRP, by = .(`raw file`)]


if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- unique(dt[, .(sequence, condition, Replicate, fraction, `raw file`)])[, .N, by = .(condition, Replicate, fraction, `raw file`)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- unique(dt[, .(sequence, condition, Replicate, `raw file`)])[, .N, by = .(condition, Replicate, `raw file`)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=`raw file`)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# Peptide Sequences") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))

```

#### With intensity values - from peptides.txt
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(pept_int[Imputed == 0])

dt[is.na(condition), condition := "Library"]

if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- dt[, .N, by = .(condition, Replicate, fraction)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt <- dt[, .N, by = .(condition, Replicate)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=Replicate)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# PSMs") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))


```


### PSMs
```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(msms)
setnames(dt, "experiment", "condition")

# check if there are any files in the msms.txt not included in the experiment design
dt[is.na(condition), condition := "Library"]
dt[condition == "Library" & is.na(Replicate), Replicate := .GRP, by = .(`raw file`)]


if ("fraction" %in% colnames(dt) && dt[, any(fraction > 0, na.rm = T)]) {
dt <- dt[, .N, by = .(condition, Replicate, fraction, `raw file`)]
dt[, Run := str_c(condition, Replicate, fraction, sep = " - ")]

} else {
dt
dt <- dt[, .N, by = .(condition, Replicate, `raw file`)]
dt[, Run := str_c(condition, Replicate, sep = " - ")]

}

g <- ggplot(dt, aes(x = as.factor(Run), y = N, color = condition, label=`raw file`)) +
  geom_segment( aes(x=as.factor(Run), xend=as.factor(Run), y=0, yend=N), color="skyblue") +
  geom_point(size=2, alpha=0.9) +
  coord_flip() +
  theme_minimal() +
  scale_x_discrete("LC-MS run") +
  scale_y_continuous("# PSMs") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
        )
ggplotly(g, tooltip = c("label", "y"))
```


