---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>




```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)

num_files <- expdes[, .N]
run_per_condition <- expdes[, .(countRepMax = .N), by = .(experiment)]
setnames(run_per_condition, "experiment", "condition")

# for fractions, create file name from mqExperiment and Fraction
if (!("file_name" %in% colnames(expdes))){
  expdes$file_name = paste(expdes$experiment, " - ", expdes$Replicate)
}


if (!protein_only){
  mod_pept_int_rep <- merge(
    run_per_condition,
    mod_pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
    by = c("condition")
  )
  mod_pept_int_rep[, repPC := Repcount/countRepMax]
  mod_pept_id_in_a_cond <- mod_pept_int_rep[repPC >= 0.5, unique(id)]
  mod_pept_int[, Valid := 0L]
  mod_pept_int[id %in% mod_pept_id_in_a_cond, Valid := 1L]
  rm(mod_pept_id_in_a_cond, mod_pept_int_rep)
  
  pept_int_rep <- merge(
    run_per_condition,
    pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
    by = c("condition")
  )
  pept_int_rep[, repPC := Repcount/countRepMax]
  pept_id_in_a_cond <- pept_int_rep[repPC >= 0.5, unique(id)]
  pept_int[, Valid := 0L]
  pept_int[id %in% pept_id_in_a_cond, Valid := 1L]
  rm(pept_id_in_a_cond, pept_int_rep)
  
}

prot_int_rep <- merge(
  run_per_condition,
  prot_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
prot_int_rep[, repPC := Repcount/countRepMax]
prot_id_in_a_cond <- prot_int_rep[repPC >= 0.5, unique(id)]
prot_int[, Valid := 0L]
prot_int[id %in% prot_id_in_a_cond, Valid := 1L]
rm(prot_id_in_a_cond, prot_int_rep)


```


```{r cv-proteins, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
cvdt <- prot_int[Imputed == 0][, countRep := .N, by = .(id, condition)]
cvdt[, countRepMax := max(countRep), by = .(id, condition)]
cvdt[, ReplicatePC := countRep/countRepMax]
cvdt[, intensity := as.double(intensity)]
cvdt <- cvdt[ReplicatePC >= 0.5, .(cv = sd(intensity)/mean(intensity)), by = .(id, condition)]

p <- ggplot(cvdt, aes(x=cv, fill=condition, colour=condition)) +
  geom_density(alpha=0.4) +
  theme_minimal() +
  scale_x_continuous("% CV", labels = scales::percent) +
  ggtitle("Proteins - LFQ intensity CV")

ggplotly(p) %>% config(displayModeBar = T, 
                        modeBarButtons = list(list('toImage')),
                        displaylogo = F)
```


