---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>



```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)

num_files <- expdes[, .N]
run_per_condition <- expdes[, .(countRepMax = .N), by = .(experiment)]
setnames(run_per_condition, "experiment", "condition")

# for fractions, create file name from mqExperiment and Fraction
if (!("file_name" %in% colnames(expdes))){
  expdes$file_name = paste(expdes$experiment, " - ", expdes$Replicate)
}


mod_pept_int_rep <- merge(
  run_per_condition,
  mod_pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
mod_pept_int_rep[, repPC := Repcount/countRepMax]
mod_pept_id_in_a_cond <- mod_pept_int_rep[repPC >= 0.5, unique(id)]
mod_pept_int[, Valid := 0L]
mod_pept_int[id %in% mod_pept_id_in_a_cond, Valid := 1L]
rm(mod_pept_id_in_a_cond, mod_pept_int_rep)

pept_int_rep <- merge(
  run_per_condition,
  pept_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
pept_int_rep[, repPC := Repcount/countRepMax]
pept_id_in_a_cond <- pept_int_rep[repPC >= 0.5, unique(id)]
pept_int[, Valid := 0L]
pept_int[id %in% pept_id_in_a_cond, Valid := 1L]
rm(pept_id_in_a_cond, pept_int_rep)

prot_int_rep <- merge(
  run_per_condition,
  prot_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
prot_int_rep[, repPC := Repcount/countRepMax]
prot_id_in_a_cond <- prot_int_rep[repPC >= 0.5, unique(id)]
prot_int[, Valid := 0L]
prot_int[id %in% prot_id_in_a_cond, Valid := 1L]
rm(prot_id_in_a_cond, prot_int_rep)


```


```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
pca_dt <- pept_int[Valid == 1, .(
  id,
  condition,
  Replicate,
  log2NInt,
  run_id
)]
```


```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

name_of_column <- colnames(pept)[colnames(pept) == "adj.P.Val"]
if (!identical(name_of_column, character(0)) && pept[get(name_of_column) <= 0.05, .N] > 1) {
  DE_ids <- pept[get(name_of_column) <= 0.05, unique(id)]
  pca_dt <- pept_int[id %in% DE_ids, .(
    id,
    condition,
    Replicate,
    log2NInt
  )]
  pca_dt <- dcast(pca_dt, condition + Replicate ~ id, value.var = "log2NInt")
  
  num_dimensions = min(pca_dt[, .N-1], 10)
  res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
  eig.val <- get_eigenvalue(res.pca)
  eig.val <- data.table(dims = rownames(eig.val), eig.val)
  
  samples.pca <- get_pca_ind(res.pca)
  samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
  samples.coord[, Run := str_c(condition, Replicate, sep = " - ")]
  
  #if no fracs
  samples.coord = merge(samples.coord, expdes, by.x = c("condition", "Replicate"), 
                        by.y = c("experiment", "Replicate"))
  label = "file_name"
  
  p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill=condition, label=Run)) +
    stat_ellipse(geom = "polygon", alpha=0.1) +
    geom_point(size = 3, alpha = 0.7) +
    theme_minimal() +
    scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
    scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%"))
    #ggtitle(str_c("PCA plot using the ", length(DE_ids), " differentially expressed peptides"))
  
  ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = T, 
                                                 modeBarButtons = list(list('toImage')),
                                                 displaylogo = F)
}
```


