---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>




```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)

num_files <- expdes[, .N]
run_per_condition <- expdes[, .(countRepMax = .N), by = .(experiment)]
setnames(run_per_condition, "experiment", "condition")

# for fractions, create file name from mqExperiment and Fraction
if (!("file_name" %in% colnames(expdes))){
  expdes$file_name = paste(expdes$experiment, " - ", expdes$Replicate)
}


prot_int_rep <- merge(
  run_per_condition,
  prot_int[Imputed == 0, .(Repcount = .N), by = .(id, condition)],
  by = c("condition")
)
prot_int_rep[, repPC := Repcount/countRepMax]
prot_id_in_a_cond <- prot_int_rep[repPC >= 0.5, unique(id)]
prot_int[, Valid := 0L]
prot_int[id %in% prot_id_in_a_cond, Valid := 1L]
rm(prot_id_in_a_cond, prot_int_rep)


```


```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
if ("file_name" %in% colnames(prot_int)){
  filenames <- prot_int[!(is.na(file_name)), unique(run_id)]
} else {
  filenames <- prot_int[, unique(run_id)]
}

int_corr_dt <- dcast.data.table(
  prot_int[Imputed == 0],
  id ~ condition + Replicate,
  value.var = "log2NInt",
  sep = "_"
)

# must have >4 observations for spearman correlation to run
test = try(rcorr(as.matrix(int_corr_dt[, 2:ncol(int_corr_dt)])), silent = TRUE)

if (class(test) != "try-error") {

  if (length(filenames) > 4) {
    filenames <- sample(filenames, 4)
  }
  
  int_corr_dt <- dcast.data.table(
    prot_int[run_id %in% filenames & Imputed == 0],
    id ~ condition + Replicate,
    value.var = "log2NInt",
    sep = "_"
  )
  
  myplot <- function(data, mapping, ...) {
    ggplot(data=data, mapping=mapping) +
      geom_point(size = 1, alpha = 0.3, colour = "skyblue2") +
      theme_minimal()
  }
  p <- ggpairs(int_corr_dt, columns = colnames(int_corr_dt)[2:ncol(int_corr_dt)],
               upper = list(
                 continuous = myplot
               ),
               lower = "blank",
               diag = NULL
  )
  p
  
} 
```
