---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>




```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(knitr)
library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)
```

```{r, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
#assert that all the stuff we need is there. 
stopifnot(exists("expdes"))
stopifnot(exists("prot"))
stopifnot(exists("prot_int"))
```


```{r eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE, results='asis'}
expdes <- expdes[,c("condition", "experiment", "reporter_channel", "replicate")]
```



```{r, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
pca_dt <- prot_int[, .(
  id,
  condition,
  replicate,
  log2NIntNorm,
  run_id
)]

pca_dt <- dcast(pca_dt, condition + replicate ~ id, value.var = "log2NIntNorm")



num_dimensions = min(pca_dt[, .N-1], 10)
res.pca <- PCA(pca_dt[, 3:ncol(pca_dt)], graph = FALSE, ncp = num_dimensions)
eig.val <- get_eigenvalue(res.pca)
eig.val <- data.table(dims = rownames(eig.val), eig.val)

samples.pca <- get_pca_ind(res.pca)
samples.coord <- data.table(pca_dt[, 1:2], samples.pca$coord)
samples.coord[, Run := str_c(condition, replicate, sep = " - ")]

p <- ggplot(samples.coord, aes(x = Dim.1, y=Dim.2, colour=condition, fill = condition, label=Run)) +
  stat_ellipse(geom = "polygon", alpha=0.1) +
  geom_point(size = 3, alpha = 0.7) +
  theme_minimal() +
  scale_x_continuous(str_c("PCA 1 - ", eig.val[dims == "Dim.1", round(variance.percent,1)], "%")) +
  scale_y_continuous(str_c("PCA 2 - ", eig.val[dims == "Dim.2", round(variance.percent,1)], "%")) +
  ggtitle("Proteins - PCA")


ggplotly(p, tooltip = c("label")) %>% config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
```