---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>




```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(knitr)
library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)
```

```{r, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
#assert that all the stuff we need is there. 
stopifnot(exists("expdes"))
stopifnot(exists("prot"))
stopifnot(exists("prot_int"))

```

```{r eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE, results='asis'}
expdes <- expdes[,c("condition", "experiment", "reporter_channel", "replicate")]
```

```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}

p <- ggplot(prot_int[Imputed==F], aes(x=interaction(reporter_channel, experiment), 
                                      y=log2NInt, fill=condition, colour=condition)) +
  geom_boxplot() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank()
  ) +
  scale_x_discrete("Channel.Run") +
  scale_y_continuous("Log2 Reporter Intensity") +
  ggtitle("Proteins - Measurements distributions")

fig <- ggplotly(p, tooltip = c("y"))%>% config(displayModeBar = T, 
                                        modeBarButtons = list(list('toImage')),
                                        displaylogo = F)


fig$x$data <- lapply(fig$x$data, FUN = function(x){
  x$marker$outliercolor = x$line$color # When creating plot p with ggplot if you specify fill = cut use x$fill$color instead of $line$color
  x$marker$color = x$line$color # When creating plot p with ggplot if you specify fill = cut use x$fill$color instead $line$color
  x$marker$line = x$line$color # When creating plot p with ggplot if you specify fill = cut use x$fill$color instead $line$color
  return(x)
})

p
```