---
title: ""
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  output_figure: figures
---

<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>



```{r eval=TRUE, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.cap = NULL, fig.path = params$output_figure)

library(knitr)
library(data.table)
library(ggplot2)
library(ggrepel)
library(GGally)
library(umap)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(viridis)
library(ggpubr)
library(Hmisc)
library(plotly)
library(stringr)
library(bit64)
```

```{r, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
evidence <- generic_mq_table_reader(upload_folder, 'evidence.txt')
```


```{r, eval=TRUE, warning=FALSE, echo=FALSE, message=FALSE, error=FALSE}
dt <- copy(evidence)

dt <- dt[, .(percent = .N), by = .(`missed cleavages`, `raw file`)]

dt[, `missed cleavages` := as.factor(`missed cleavages`)]
p <- ggplot(dt, aes(x = `raw file`, y = percent,  fill=`missed cleavages`, label=`raw file`)) +
  geom_bar(stat="identity", position=position_fill(reverse = TRUE)) +
  theme_minimal() +
  scale_y_continuous("% missed c leavages", labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2),
        panel.grid.major.y = element_blank(),
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "top"
  ) +
  labs(fill = "Missed\nCleavages")

  ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = T, 
                                           modeBarButtons = list(list('toImage')),
                                           displaylogo = F)
```
